\bf Manifold Clustering in the Generalized Random Dot Product Graph

### 2022-05-18 draft/draft.Rmd
still working on proofs

\begin{theorem}[Community detection for nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Define $A_n$ as the event that for a $\eta$-neighborhood graph constructed from the sample $x_1, ..., x_n$ consists of exactly $K$ disconnected subgraphs that map on exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $A_n$ occurs with high probability. 
\label{nonintersect-no-noise}
\end{theorem}

>>>>

\begin{theorem}[Community detection for nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Define $A_n$ as the event that a $\eta$-neighborhood graph constructed from the sample $x_1, ..., x_n$ consists of exactly $K$ disconnected subgraphs that map exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}{Community detection for RDPG for which the communities come from nonintersecting manifolds}
\label{nonintersect-rdpg}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$ and $A \sim \RDPG(X)$. 
Define $B_n$ as the event that an $\eta$-neighborhood graph constructed from the ASE of $A$ consists of exactly $K$ disconnected subgraphs that map exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}

### 2022-05-18 draft/draft.tex
still working on proofs

\begin{theorem}[Community detection for nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Define $A_n$ as the event that for a $\eta$-neighborhood graph constructed from the sample $x_1, ..., x_n$ consists of exactly $K$ disconnected subgraphs that map on exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $A_n$ occurs with high probability. 
\label{nonintersect-no-noise}
\end{theorem}

>>>>

\begin{theorem}[Community detection for nonintersecting manifolds without noise]
\label{nonintersect-no-noise}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Define $A_n$ as the event that a $\eta$-neighborhood graph constructed from the sample $x_1, ..., x_n$ consists of exactly $K$ disconnected subgraphs that map exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $P(A_n) > 1 - \epsilon$. 
\end{theorem}

\begin{theorem}{Community detection for RDPG for which the communities come from nonintersecting manifolds}
\label{nonintersect-rdpg}
Let $x_1, ..., x_n$ be points sampled on $K$ manifolds $\mathcal{M}_1, ..., \mathcal{M}_K$. 
Suppose $\delta = \min\limits_{k \neq \ell} \min\limits_{x_i \in \mathcal{M}_k, x_j \in \mathcal{M}_\ell} \| x_i - x_j \| > 0$. 
Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$ and $A \sim \mathrm{RDPG}(X)$. 
Define $B_n$ as the event that an $\eta$-neighborhood graph constructed from the ASE of $A$ consists of exactly $K$ disconnected subgraphs that map exactly to each manifold for some $\eta \in (0, \delta)$. 
Then for any $\epsilon \in (0, 1)$, there exists an $N$ such that when $n > N$, $P(B_n) > 1 - \epsilon$. 
\end{theorem}
